---
title: "analyses_supplement"
author: "Lieke Hofmans"
date: "6/15/2020"
output: pdf_document
---

This script runs the analyses of which the results are presented in the supplement of "Methylphenidate boosts choices of mental labor over leisure depending on striatal dopamine synthesis capacity".  

indep. variables: drug, set size, task type (condition), ki
N = 46 


Load libraries
```{r}
# you probably don't need all of these packages, but I just c/p most of them from other scripts I ran recently. 
library(tidyverse)
library(afex)
library(car)
library(reshape)
library(ez)
library(dplyr)
library(readr)
library(tidyr)
library(outliers)
library(MOTE)
```


set up (calls set up script)

```{r}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
source("set_up.R")

df_choice <- df_choice[complete.cases(df_choice$wholePutamen),]
df_choice$condition_IU <- as.factor(df_choice$condition_IU)
df_choice$set_size <- as.factor(df_choice$set_size)
df_choice$easy_offer <- as.factor(df_choice$easy_offer)

df_colorwheel <- df_colorwheel[complete.cases(df_colorwheel$wholePutamen),]
df_colorwheel$condition <- as.factor(df_colorwheel$condition)
df_colorwheel$set_size <- as.factor(df_colorwheel$set_size)

```

Per session, participants had to complete 288 choice trials, divided over 4 set sizes and 2 task type, which resulted in 36 trials for each of those combinations. 
On those 36 trials, the offer for redo was fixed at 2 euro. The offer for no redo varied as c(0.10, 0.20, 0.40, 0.60, 0.80, 1.00, 1.20, 1.40, 1.60, 1.80, 2.00, 2.20) (= 12 different values). Each offer was presented 3 times. 

Analyses are run separately for each ROI (putamen, caudate, nucleus accumbens/ventral striatum). dopamine-independent effects are taken from the analysis including putamen ki (Lieke's random choice). 



Effects on proportion redo choices are reproduced when analysing indifferent points

```{r}
# IP

# At baseline, participants exhibited a strong preference for not repeating the task, as evidenced by the overall IP being significantly smaller than €2.00
temp <- allDepVars_wide_drug
temp <- temp[complete.cases(as.numeric(temp$VS_mc)),]
ttest <- t.test(temp$IP_PBO, mu = 2)
d.single.t(ttest$estimate, ttest$null.value, sd(temp$IP_PBO), length(temp$IP_PBO), .05)

# only select IP and Ki columns
temp <- allDepVars_wide_drug
temp <- temp %>%
  dplyr::select(sID, grep("IP", colnames(temp)), wholePutamen_mc, wholeCaudate_mc, VS_mc)
names(temp) = gsub(pattern = "IP_*", replacement = "", x = names(temp))

# flip from wide to long
temp <- temp %>%  
  pivot_longer(c("PBO_I_1", "PBO_I_2",	"PBO_I_3",	"PBO_I_4", "MPH_I_1",	"MPH_I_2",	"MPH_I_3","MPH_I_4","SUL_I_1","SUL_I_2","SUL_I_3","SUL_I_4","PBO_U_1","PBO_U_2","PBO_U_3","PBO_U_4","MPH_U_1","MPH_U_2","MPH_U_3","MPH_U_4","SUL_U_1","SUL_U_2","SUL_U_3","SUL_U_4"), names_to = "condition", values_to = "IP") %>%
  separate(condition, into = c("drug", "condition_IU", "set_size"))
temp$wholePutamen_mc <- as.numeric(temp$wholePutamen_mc)
temp$wholeCaudate_mc <- as.numeric(temp$wholeCaudate_mc)
temp$VS_mc <- as.numeric(temp$VS_mc)
temp$drug <- as.factor(temp$drug)
temp$condition_IU <- as.factor(temp$condition_IU)
temp$set_size <- as.factor(temp$set_size)

# remove participants without pet data
temp <- temp[complete.cases(temp$VS_mc),]


# putamen
aov <- aov_car(IP ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = temp, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["set_size","num Df"], # set_size
    dfe = summary(aov)[[4]]["set_size","den Df"],
    ssm = summary(aov)[[4]]["set_size","Sum Sq"],
    sse = summary(aov)[[4]]["set_size","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["condition_IU","num Df"], # task type
    dfe = summary(aov)[[4]]["condition_IU","den Df"],
    ssm = summary(aov)[[4]]["condition_IU","Sum Sq"],
    sse = summary(aov)[[4]]["condition_IU","Error SS"],
    Fvalue = summary(aov)[[4]]["condition_IU","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["set_size:condition_IU","num Df"], # set size by task type
    dfe = summary(aov)[[4]]["set_size:condition_IU","den Df"],
    ssm = summary(aov)[[4]]["set_size:condition_IU","Sum Sq"],
    sse = summary(aov)[[4]]["set_size:condition_IU","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size:condition_IU","F value"],
    a = .1)[8]

    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
    dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
    a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(IP ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="SUL",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
        dfe = summary(aov)[[4]]["drug","den Df"],
        ssm = summary(aov)[[4]]["drug","Sum Sq"],
        sse = summary(aov)[[4]]["drug","Error SS"],
        Fvalue = summary(aov)[[4]]["drug","F value"],
        a = .1)[8]
    
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(IP ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="MPH",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
        dfe = summary(aov)[[4]]["drug","den Df"],
        ssm = summary(aov)[[4]]["drug","Sum Sq"],
        sse = summary(aov)[[4]]["drug","Error SS"],
        Fvalue = summary(aov)[[4]]["drug","F value"],
        a = .1)[8]    
    
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(IP ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="PBO",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
        dfe = summary(aov)[[4]]["drug","den Df"],
        ssm = summary(aov)[[4]]["drug","Sum Sq"],
        sse = summary(aov)[[4]]["drug","Error SS"],
        Fvalue = summary(aov)[[4]]["drug","F value"],
        a = .1)[8]    
    
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(IP ~ wholePutamen_mc + Error(sID/(set_size*condition_IU)), data = temp[temp$drug=="PBO",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc","num Df"], # drug
        dfe = summary(aov)[[4]]["wholePutamen_mc","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc","F value"],
        a = .1)[8]
 
        
# caudate
aov <- aov_car(IP ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = temp, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
    dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
    a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(IP ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="SUL",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(IP ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="MPH",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(IP ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="PBO",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(IP ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU)), data = temp[temp$drug=="PBO",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc","num Df"], # drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc","F value"],
        a = .1)[8]

        
# VS
aov <- aov_car(IP ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = temp, observed = "VS_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
    dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
    a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(IP ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="SUL",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(IP ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="MPH",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(IP ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = temp[temp$drug!="PBO",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(IP ~ VS_mc + Error(sID/(set_size*condition_IU)), data = temp[temp$drug=="PBO",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc","num Df"], # drug
        dfe = summary(aov)[[4]]["VS_mc","den Df"],
        ssm = summary(aov)[[4]]["VS_mc","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc","F value"],
        a = .1)[8] 
```


Methylphenidate-induced effect does not reflect choice randomness
```{r, fig.height=8, fig.width=8}

# slope

# select data and flip dataframe from wide to long
temp <- allDepVars_wide_drug
temp <- temp %>%
  dplyr::select(sID, slope_Total, slope_MPH, slope_PBO, wholePutamen_mc, wholeCaudate_mc, VS_mc)
names(temp) = gsub(pattern = "slope_*", replacement = "", x = names(temp))
temp <- temp %>%  
  pivot_longer(c("MPH", "PBO"), names_to = "drug", values_to = "slope")
temp$wholePutamen_mc <- as.numeric(temp$wholePutamen_mc)
temp$wholeCaudate_mc <- as.numeric(temp$wholeCaudate_mc)
temp$VS_mc <- as.numeric(temp$VS_mc)
temp$slope <- as.numeric(temp$slope)
temp$Total <- as.numeric(temp$Total)
temp$drug <- as.factor(temp$drug)

# remove people with incomplete data
temp <- temp[complete.cases(temp$slope) & complete.cases(temp$VS_mc),]
for (jj in unique(temp$sID)){
  if (sum(temp$sID==jj) < 2){
    temp <- temp[temp$sID!=jj, ]  
  }
}

# any outliers on overall slope?
max <- mean(as.numeric(temp$Total), na.rm=T) + 3*sd(as.numeric(temp$Total), na.rm=T)
min <- mean(as.numeric(temp$Total), na.rm=T) - 3*sd(as.numeric(temp$Total), na.rm=T)
temp <- temp[which(temp$Total < max & temp$Total > min),] # who exceeds threshold; pp 9 + 21




# putamen
aov <- aov_car(slope ~ wholePutamen_mc + Error(sID/(drug)), data = temp, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)  
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
    dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

# caudate
aov <- aov_car(slope ~ wholeCaudate_mc + Error(sID/(drug)), data = temp, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
    dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
    a = .1)[8]

# VS
aov <- aov_car(slope ~ VS_mc + Error(sID/(drug)), data = temp, observed = "VS_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
    dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
    a = .1)[8]

   


```






Dopamine synthesis capacity-dependent effects cannot be explained by working-memory performance

```{r, fig.height=8, fig.width=8}

# Deviance
temp <- df_colorwheel
summ <- summarySE(temp, measurevar="abs_deviance", groupvars=c("sID", "set_size", "condition", "drug", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc"))


# putamen
aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition*drug)), data = summ, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
    dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

# caudate
aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition*drug)), data = summ, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
    dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
    a = .1)[8]

# VS
aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition*drug)), data = summ, observed = "VS_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
    dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
    a = .1)[8]

   



# RT
temp <- df_colorwheel
summ <- summarySE(temp, measurevar="RT", groupvars=c("sID", "set_size", "condition", "drug", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc"))


# putamen
aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition*drug)), data = summ, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
    dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

# caudate
aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition*drug)), data = summ, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
    dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
    a = .1)[8]

# VS
aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition*drug)), data = summ, observed = "VS_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
    dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
    a = .1)[8]



```




No correlation between MPH-induced effects on performance vs cognitive motivation and choice latency
```{r, fig.height=8, fig.width=8}

# calculate difference scores
ratioRedo <- summarySE(df_choice, measurevar="choice_NR", groupvars=c("sID", "drug"))
ratioRedo <- ratioRedo %>%
  dplyr::select(sID, drug, choice_NR) %>%
  spread(drug, choice_NR)
ratioRedo$MPH_effect <- ratioRedo$MPH - ratioRedo$PBO

RTchoice <- summarySE(df_choice, measurevar="RT", groupvars=c("sID", "drug"))
RTchoice <- RTchoice %>%
  dplyr::select(sID, drug, median) %>%
  spread(drug, median)
RTchoice$MPH_effect <- RTchoice$MPH - RTchoice$PBO

deviance <- summarySE(df_colorwheel, measurevar="abs_deviance", groupvars=c("sID", "drug"))
deviance <- deviance %>%
  dplyr::select(sID, drug, median) %>%
  spread(drug, median)
deviance$MPH_effect <- deviance$MPH - deviance$PBO

RT <- summarySE(df_colorwheel, measurevar="RT", groupvars=c("sID", "drug"))
RT <- RT %>%
  dplyr::select(sID, drug, median) %>%
  spread(drug, median)
RT$MPH_effect <- RT$MPH - RT$PBO



# MPH - PBO
corMPH <- cor.test(deviance$MPH_effect, ratioRedo$MPH_effect) 
print(corMPH, digits = 3)
print(corMPH$p.value, digits = 3)

corMPH <- cor.test(deviance$MPH_effect, RTchoice$MPH_effect) 
print(corMPH, digits = 3)
print(corMPH$p.value, digits = 3)

corMPH <- cor.test(RT$MPH_effect, ratioRedo$MPH_effect) 
print(corMPH, digits = 3)
print(corMPH$p.value, digits = 3)

corMPH <- cor.test(RT$MPH_effect, RTchoice$MPH_effect) 
print(corMPH, digits = 3)
print(corMPH$p.value, digits = 3)

```




Baseline dopamine synthesis capacity-dependent effects cannot be explained by mood and medical symptoms 

```{r}

# MANOVAs were run in SPSS
# Here, I calculate the correlations between the MPH effect on ratio redo and the MPH effect on the mood and medical measures (at timepoint 2).

# only select mood and medical symptoms and pivot to long format
temp <- dplyr::select(medical_mood_phys, c(vID, panasNeg_MPH_1:vasMedical_SUL_3)) 
temp$VS_mc <- as.numeric(allDepVars_wide_drug$VS_mc)
temp <- temp[complete.cases(temp$VS_mc),]
temp <- temp %>%
  pivot_longer(c(panasNeg_MPH_1:vasMedical_SUL_3), names_to="measure", values_to = "value") %>%
  separate(measure, into = c("measure", "drug", "timepoint")) %>%
  pivot_wider(names_from = measure, values_from = value)

temp$drug <- as.factor(temp$drug)
temp$timepoint <- as.factor(temp$timepoint)
temp <- temp[temp$timepoint==2 & temp$drug!="SUL",] # only interested at timepoint 2 for PBO and MPH here

MPH_effects <- data.frame(matrix(ncol = 8, nrow = 46)) 
MPH_effects[1] <- allDepVars_wide_drug$sID[complete.cases(as.numeric(allDepVars_wide_drug$VS_mc))]
MPH_effects[2] <- (aggregate(panasNeg ~ vID, data=temp, diff) * -1)[2] 
MPH_effects[3] <- (aggregate(panasPos ~ vID, data=temp, diff) * -1)[2]
MPH_effects[4] <- (aggregate(vasAlert ~ vID, data=temp, diff) * -1)[2] 
MPH_effects[5] <- (aggregate(vasCalm ~ vID, data=temp, diff) * -1)[2] 
MPH_effects[6] <- (aggregate(vasContend ~ vID, data=temp, diff) * -1)[2] 
MPH_effects[7] <- (aggregate(vasMedical ~ vID, data=temp, diff) * -1)[2] 
MPH_effects[8] <- allDepVars_wide_drug$ratioRedo_MPH[complete.cases(as.numeric(allDepVars_wide_drug$VS_mc))] - allDepVars_wide_drug$ratioRedo_PBO[complete.cases(as.numeric(allDepVars_wide_drug$VS_mc))]
names(MPH_effects) <- c("sID", "panasNeg", "panasPos", "vasAlert", "vasCalm", "vasContend", "vasMedical", "ratioRedo")

# run correlations
cor <- cor.test(MPH_effects$panasNeg, MPH_effects$ratioRedo) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(MPH_effects$panasPos, MPH_effects$ratioRedo) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(MPH_effects$vasAlert, MPH_effects$ratioRedo) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(MPH_effects$vasCalm, MPH_effects$ratioRedo) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(MPH_effects$vasContend, MPH_effects$ratioRedo) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(MPH_effects$vasMedical, MPH_effects$ratioRedo) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)


# run additional rmANOVA including MPH effect on positive affect and alertness as covariates

temp <- df_choice
# add MPH effects on pos and alert to temp 
for (jj in MPH_effects$sID){
  temp[temp[,"sID"]==jj,"MPH_effect_panasPos_mc"] <- MPH_effects[MPH_effects[,"sID"]==jj,"panasPos"] - mean(MPH_effects$panasPos)
  temp[temp[,"sID"]==jj,"MPH_effect_vasAlert_mc"] <- MPH_effects[MPH_effects[,"sID"]==jj,"vasAlert"] - mean(MPH_effects$vasAlert)
} 

summ <- summarySE(temp, measurevar="choice_NR", groupvars=c("sID", "set_size", "condition_IU", "drug", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc", "MPH_effect_panasPos_mc", "MPH_effect_vasAlert_mc"))


# POSITIVE AFFECT
# putamen
aov <- aov_car(choice_NR ~ wholePutamen_mc + MPH_effect_panasPos_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
        dfe = summary(aov)[[4]]["drug","den Df"],
        ssm = summary(aov)[[4]]["drug","Sum Sq"],
        sse = summary(aov)[[4]]["drug","Error SS"],
        Fvalue = summary(aov)[[4]]["drug","F value"],
        a = .1)[8]

        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]

# caudate
aov <- aov_car(choice_NR ~ wholeCaudate_mc + MPH_effect_panasPos_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]

# VS
aov <- aov_car(choice_NR ~ VS_mc + MPH_effect_panasPos_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "VS_mc", factorize = FALSE)
summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]


# ALERTNESS
# putamen
aov <- aov_car(choice_NR ~ wholePutamen_mc + MPH_effect_vasAlert_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
        dfe = summary(aov)[[4]]["drug","den Df"],
        ssm = summary(aov)[[4]]["drug","Sum Sq"],
        sse = summary(aov)[[4]]["drug","Error SS"],
        Fvalue = summary(aov)[[4]]["drug","F value"],
        a = .1)[8]

        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]

# caudate
aov <- aov_car(choice_NR ~ wholeCaudate_mc + MPH_effect_vasAlert_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]

# VS
aov <- aov_car(choice_NR ~ VS_mc + MPH_effect_vasAlert_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "VS_mc", factorize = FALSE)
summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]


```




Controlling for session order

A first ANOVA confirmed that session-day-number (1, 2 or 3) did not differ between the three drugs

```{r}

# only select session numbers and Ki
temp <- allDepVars_wide_drug
temp <- temp %>%
  dplyr::select(MPH, SUL, PBO, VS_mc) %>%
  pivot_longer(c("PBO", "MPH", "SUL"), names_to = "drug", values_to = "day")
# remove participants without pet data
temp <- temp[complete.cases(as.numeric(temp$VS_mc)),]
# add row number
temp$row <- c(1:length(temp$drug))

aov <- aov_car(day ~ drug + Error(row), data = temp, factorize = T)
aov$aov
    # (partial) eta sq + 90%CI
    eta.partial.SS(dfm = 2, 
    dfe = 135,
    ssm = 1.17,
    sse = 90.83,
    Fvalue = 0.42,
    a = .1)[8]



```


Unexpectedly, a Spearman’s rank correlation indeed revealed that dopamine synthesis capacity was negatively correlated with the session on which participants received methylphenidate (Table S8). 

```{r}

# only select session numbers and Ki
temp <- allDepVars_wide_drug
temp <- temp %>%
  dplyr::select(MPH, SUL, PBO, VS, wholePutamen, wholeCaudate) 
# remove participants without pet data
temp <- temp[complete.cases(as.numeric(temp$VS)),]
temp$VS <- as.numeric(temp$VS)
temp$wholePutamen <- as.numeric(temp$wholePutamen)
temp$wholeCaudate <- as.numeric(temp$wholeCaudate)

# Spearmans rank correlation between ki and session number

# putamen
cor <- cor.test(temp$wholePutamen, temp$MPH, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(temp$wholePutamen, temp$SUL, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(temp$wholePutamen, temp$PBO, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

# caudate
cor <- cor.test(temp$wholeCaudate, temp$MPH, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(temp$wholeCaudate, temp$SUL, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(temp$wholeCaudate, temp$PBO, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

# VS
cor <- cor.test(temp$VS, temp$MPH, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(temp$VS, temp$SUL, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(temp$VS, temp$PBO, method = "spearman") 
print(cor, digits = 3)
print(cor$p.value, digits = 3)


```


Dopamine synthesis capacity-dependent effects are smaller, but still qualitatively present when controlling for session order

```{r}

# ratio redo

temp <- df_choice
summ <- summarySE(temp, measurevar="choice_NR", groupvars=c("sID", "set_size", "condition_IU", "drug", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc", "MPH"))
summ$MPH <- as.factor(summ$MPH)

# putamen
# comparison between MPH and PBO
aov <- aov_car(choice_NR ~ wholePutamen_mc + MPH + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholePutamen_mc", factorize = FALSE)
summary(aov) 


    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
    dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
    a = .1)[8]

# caudate
# comparison between MPH and PBO
aov <- aov_car(choice_NR ~ wholeCaudate_mc + MPH + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
    dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
    a = .1)[8]

# VS
# comparison between MPH and PBO
aov <- aov_car(choice_NR ~ VS_mc + MPH + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "VS_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
    dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
    a = .1)[8]

   
    

# choice latency

temp <- df_choice
summ <- summarySE(temp, measurevar="RT", groupvars=c("sID", "set_size", "condition_IU", "drug", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc", "MPH"))
summ$MPH <- as.factor(summ$MPH)

# putamen
# comparison between MPH and PBO
aov <- aov_car(median ~ wholePutamen_mc + MPH + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
    dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
    a = .1)[8]

# caudate
# comparison between MPH and PBO
aov <- aov_car(median ~ wholeCaudate_mc + MPH + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
    dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
    a = .1)[8]

# VS
# comparison between MPH and PBO
aov <- aov_car(median ~ VS_mc + MPH + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "VS_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
    dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
    a = .1)[8]
    
   

```


No correlation between dopamine synthesis capacity and time after methylphenidate administration

```{r}

# only select days between PET scan and the MPH session and Ki
temp <- allDepVars_wide_drug
temp <- temp %>%
  dplyr::select(MPH_PET, VS, wholePutamen, wholeCaudate) 
# remove participants without pet data
temp <- temp[complete.cases(as.numeric(temp$VS)),]
temp$VS <- as.numeric(temp$VS)
temp$wholePutamen <- as.numeric(temp$wholePutamen)
temp$wholeCaudate <- as.numeric(temp$wholeCaudate)
temp$MPH_PET <- as.numeric(temp$MPH_PET)

# Pearsons correlation between ki and MPH_PET
cor <- cor.test(temp$wholePutamen, temp$MPH_PET) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(temp$wholeCaudate, temp$MPH_PET) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)

cor <- cor.test(temp$VS, temp$MPH_PET) 
print(cor, digits = 3)
print(cor$p.value, digits = 3)


```



ANALYZED IN SPSS:
Baseline dDopamine synthesis capacity-dependent effects cannot be explained by mood and medical symptoms: MANOVA 
Drug effects on physiological measures: MANOVA


