---
title: "analyses_manuscript"
author: "Lieke Hofmans"
date: "6/15/2020"
output: pdf_document
---



This script runs the analyses of which the results are presented in the main text of "Methylphenidate boosts choices of mental labor over leisure depending on striatal dopamine synthesis capacity".  

indep. variables: drug, set size, task type (condition), ki
N = 46 


Load libraries
```{r}
# you probably don't need all of these packages, but I just c/p most of them from other scripts I ran recently. 
library(tidyverse)
library(afex)
library(car)
library(reshape)
library(ez)
library(dplyr)
library(readr)
library(tidyr)
library(outliers)
library(MOTE)
```


set up (calls set up script)

```{r}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
source("set_up.R")

df_choice <- df_choice[complete.cases(df_choice$wholePutamen),]
df_choice$condition_IU <- as.factor(df_choice$condition_IU)
df_choice$set_size <- as.factor(df_choice$set_size)
df_choice$easy_offer <- as.factor(df_choice$easy_offer)

df_colorwheel <- df_colorwheel[complete.cases(df_colorwheel$wholePutamen),]
df_colorwheel$condition <- as.factor(df_colorwheel$condition)
df_colorwheel$set_size <- as.factor(df_colorwheel$set_size)

```

Per session, participants had to complete 288 choice trials, divided over 4 set sizes and 2 task type, which resulted in 36 trials for each of those combinations. 
On those 36 trials, the offer for redo was fixed at 2 euro. The offer for no redo varied as c(0.10, 0.20, 0.40, 0.60, 0.80, 1.00, 1.20, 1.40, 1.60, 1.80, 2.00, 2.20) (= 12 different values). Each offer was presented 3 times. 

Analyses are run separately for each ROI (putamen, caudate, nucleus accumbens/ventral striatum). dopamine-independent effects are taken from the analysis including putamen ki (Lieke's random choice). 



Working memory performance (across drug sessions)

```{r, fig.height=8, fig.width=8}

# Deviance
temp <- df_colorwheel
summ <- summarySE(temp, measurevar="abs_deviance", groupvars=c("sID", "set_size", "condition", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc"))


aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition)), data = summ, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["set_size","num Df"], # set size 
    dfe = summary(aov)[[4]]["set_size","den Df"],
    ssm = summary(aov)[[4]]["set_size","Sum Sq"],
    sse = summary(aov)[[4]]["set_size","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["condition","num Df"], # task type
    dfe = summary(aov)[[4]]["condition","den Df"],
    ssm = summary(aov)[[4]]["condition","Sum Sq"],
    sse = summary(aov)[[4]]["condition","Error SS"],
    Fvalue = summary(aov)[[4]]["condition","F value"],
    a = .1)[8]

    eta.partial.SS(dfm = summary(aov)[[4]]["set_size:condition","num Df"], # task type by set size
    dfe = summary(aov)[[4]]["set_size:condition","den Df"],
    ssm = summary(aov)[[4]]["set_size:condition","Sum Sq"],
    sse = summary(aov)[[4]]["set_size:condition","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size:condition","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc","num Df"], # putamen ki
    dfe = summary(aov)[[4]]["wholePutamen_mc","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc","F value"],
    a = .1)[8]

aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition)), data = summ, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)

    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc","num Df"], # caudate ki
    dfe = summary(aov)[[4]]["wholeCaudate_mc","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc","F value"],
    a = .1)[8]
    
aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition)), data = summ, observed = "VS_mc", factorize = FALSE)
summary(aov)

    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc","num Df"], # VS ki
    dfe = summary(aov)[[4]]["VS_mc","den Df"],
    ssm = summary(aov)[[4]]["VS_mc","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc","F value"],
    a = .1)[8]



# RT
temp <- df_colorwheel
summ <- summarySE(temp, measurevar="RT", groupvars=c("sID", "set_size", "condition", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc"))


aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition)), data = summ, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov) 
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["set_size","num Df"], # set size 
    dfe = summary(aov)[[4]]["set_size","den Df"],
    ssm = summary(aov)[[4]]["set_size","Sum Sq"],
    sse = summary(aov)[[4]]["set_size","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["condition","num Df"], # task type
    dfe = summary(aov)[[4]]["condition","den Df"],
    ssm = summary(aov)[[4]]["condition","Sum Sq"],
    sse = summary(aov)[[4]]["condition","Error SS"],
    Fvalue = summary(aov)[[4]]["condition","F value"],
    a = .1)[8]

    eta.partial.SS(dfm = summary(aov)[[4]]["set_size:condition","num Df"], # task type by set size
    dfe = summary(aov)[[4]]["set_size:condition","den Df"],
    ssm = summary(aov)[[4]]["set_size:condition","Sum Sq"],
    sse = summary(aov)[[4]]["set_size:condition","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size:condition","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc","num Df"], # putamen ki
    dfe = summary(aov)[[4]]["wholePutamen_mc","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc","F value"],
    a = .1)[8]

aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition)), data = summ, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov) 

    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc","num Df"], # caudate ki
    dfe = summary(aov)[[4]]["wholeCaudate_mc","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc","F value"],
    a = .1)[8]
    
aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition)), data = summ, observed = "VS_mc", factorize = FALSE)
summary(aov)

    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc","num Df"], # VS ki
    dfe = summary(aov)[[4]]["VS_mc","den Df"],
    ssm = summary(aov)[[4]]["VS_mc","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc","F value"],
    a = .1)[8]




```


Methylphenidate increased cognitive motivation 

```{r, fig.height=8, fig.width=8}

# At baseline, participants exhibited a preference for not repeating any task, as evidenced by the overall proportion redo being significantly smaller than 0.5 on the placebo session
temp <- df_choice
summ <- summarySE(temp[temp$drug=="PBO",], measurevar="choice_NR", groupvars=c("sID")) 

ttest <- t.test(summ$choice_NR, mu = 0.5)
d.single.t(ttest$estimate, ttest$null.value, sd(summ$choice_NR), length(summ$choice_NR), .05)



# Methylphenidate increased cognitive motivation
temp <- df_choice
summ <- summarySE(temp, measurevar="choice_NR", groupvars=c("sID", "set_size", "condition_IU", "drug", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc"))

aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)

    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

    eta.partial.SS(dfm = summary(aov)[[4]]["set_size","num Df"], # set size 
    dfe = summary(aov)[[4]]["set_size","den Df"],
    ssm = summary(aov)[[4]]["set_size","Sum Sq"],
    sse = summary(aov)[[4]]["set_size","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["condition_IU","num Df"], # task type
    dfe = summary(aov)[[4]]["condition_IU","den Df"],
    ssm = summary(aov)[[4]]["condition_IU","Sum Sq"],
    sse = summary(aov)[[4]]["condition_IU","Error SS"],
    Fvalue = summary(aov)[[4]]["condition_IU","F value"],
    a = .1)[8]

    eta.partial.SS(dfm = summary(aov)[[4]]["set_size:condition_IU","num Df"], # task type by set size
    dfe = summary(aov)[[4]]["set_size:condition_IU","den Df"],
    ssm = summary(aov)[[4]]["set_size:condition_IU","Sum Sq"],
    sse = summary(aov)[[4]]["set_size:condition_IU","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size:condition_IU","F value"],
    a = .1)[8]
    
    eta.partial.SS(dfm = summary(aov)[[4]]["set_size:drug","num Df"], # set size by drug
    dfe = summary(aov)[[4]]["set_size:drug","den Df"],
    ssm = summary(aov)[[4]]["set_size:drug","Sum Sq"],
    sse = summary(aov)[[4]]["set_size:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["set_size:drug","F value"],
    a = .1)[8]  
    
    eta.partial.SS(dfm = summary(aov)[[4]]["condition_IU:drug","num Df"], # task type by drug
    dfe = summary(aov)[[4]]["condition_IU:drug","den Df"],
    ssm = summary(aov)[[4]]["condition_IU:drug","Sum Sq"],
    sse = summary(aov)[[4]]["condition_IU:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["condition_IU:drug","F value"],
    a = .1)[8]

    
# comparison between MPH and PBO
aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

# comparison between SUL and PBO
aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="MPH",], observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

    
# comparison between MPH and SUL
aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="PBO",], observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]
 
     
```


High-dopamine participants exhibited greater methylphenidate-related increases in cognitive motivation 
```{r, fig.height=8, fig.width=8}

# High-dopamine participants exhibited greater methylphenidate-related increases in cognitive motivation 

temp <- df_choice
summ <- summarySE(temp, measurevar="choice_NR", groupvars=c("sID", "set_size", "condition_IU", "drug", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc"))


# putamen
aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
    dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
    a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="MPH",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="PBO",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU)), data = summ[summ$drug=="PBO",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc","num Df"], # drug
        dfe = summary(aov)[[4]]["wholePutamen_mc","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc","F value"],
        a = .1)[8]
 
        
# caudate
aov <- aov_car(choice_NR ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = summ, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
    dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
    a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(choice_NR ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(choice_NR ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="MPH",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(choice_NR ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="PBO",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(choice_NR ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU)), data = summ[summ$drug=="PBO",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc","num Df"], # drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc","F value"],
        a = .1)[8]

        
# VS
aov <- aov_car(choice_NR ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = summ, observed = "VS_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
    dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
    a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(choice_NR ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(choice_NR ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="MPH",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(choice_NR ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="PBO",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(choice_NR ~ VS_mc + Error(sID/(set_size*condition_IU)), data = summ[summ$drug=="PBO",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc","num Df"], # drug
        dfe = summary(aov)[[4]]["VS_mc","den Df"],
        ssm = summary(aov)[[4]]["VS_mc","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc","F value"],
        a = .1)[8] 
```


Drug manipulation does not interact with the benefit of engaging in a cognitive task 
```{r, fig.height=8, fig.width=8}

temp <- df_choice
temp$offer_tertile <- as.factor(dplyr::ntile(temp$easy_offer,3))


# ratio redo
summ <- summarySE(temp, measurevar="choice_NR", groupvars=c("sID", "set_size", "condition_IU", "drug", "offer_tertile", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc"))

# putamen
aov <- aov_car(choice_NR ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug*offer_tertile)), data = summ, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)

        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["offer_tertile","num Df"], # offer_tertile
        dfe = summary(aov)[[4]]["offer_tertile","den Df"],
        ssm = summary(aov)[[4]]["offer_tertile","Sum Sq"],
        sse = summary(aov)[[4]]["offer_tertile","Error SS"],
        Fvalue = summary(aov)[[4]]["offer_tertile","F value"],
        a = .1)[8]
        
        eta.partial.SS(dfm = summary(aov)[[4]]["drug:offer_tertile","num Df"], # drug:offer_tertile
        dfe = summary(aov)[[4]]["drug:offer_tertile","den Df"],
        ssm = summary(aov)[[4]]["drug:offer_tertile","Sum Sq"],
        sse = summary(aov)[[4]]["drug:offer_tertile","Error SS"],
        Fvalue = summary(aov)[[4]]["drug:offer_tertile","F value"],
        a = .1)[8]
        
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug:offer_tertile","num Df"], # wholePutamen_mc:drug:offer_tertile
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug:offer_tertile","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug:offer_tertile","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug:offer_tertile","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug:offer_tertile","F value"],
        a = .1)[8]

# caudate
aov <- aov_car(choice_NR ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug*offer_tertile)), data = summ, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)

        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug:offer_tertile","num Df"], # wholeCaudate_mc:drug:offer_tertile
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug:offer_tertile","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug:offer_tertile","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug:offer_tertile","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug:offer_tertile","F value"],
        a = .1)[8]
   
# VS
aov <- aov_car(choice_NR ~ VS_mc + Error(sID/(set_size*condition_IU*drug*offer_tertile)), data = summ, observed = "VS_mc", factorize = FALSE)
summary(aov)

        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug:offer_tertile","num Df"], # VS_mc:drug:offer_tertile
        dfe = summary(aov)[[4]]["VS_mc:drug:offer_tertile","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug:offer_tertile","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug:offer_tertile","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug:offer_tertile","F value"],
        a = .1)[8]
 
        
        
        
# plot drug by offer tertile effect
summ <- summarySE(temp[temp$drug!="SUL",], measurevar="choice_NR", groupvars=c("sID", "drug", "offer_tertile"))
summ2 <- summarySE(summ, measurevar="choice_NR", groupvars=c("drug", "offer_tertile"))

  # lines
  ggplot(data = summ2, aes(x = as.numeric(offer_tertile), y = choice_NR, color = as.factor(drug))) +
    geom_point(data = summ, size=2, alpha=0.3, position=position_jitterdodge(jitter.width = 0.1, jitter.height=0.01, dodge.width=0.3)) +
    geom_line(size=1.5) +
    geom_errorbar(aes(ymin=choice_NR-ci, ymax=choice_NR+ci), width=.08, size=1, color = "black") +
    theme_classic(base_size = 30) +
    ylab("proportion redo choices")  +
    scale_x_continuous(name = "offer", limits=c(0.5, 3.5), labels=c("1" = "low", "2" = "medium", "3" = "high"), breaks=c(1,2,3))





```





High-dopamine participants exhibited greater methylphenidate-related slowing of choice latency
```{r, fig.height=8, fig.width=8}

# High-dopamine participants exhibited greater methylphenidate-related increases in cognitive motivation 

temp <- df_choice
summ <- summarySE(temp, measurevar="RT", groupvars=c("sID", "set_size", "condition_IU", "drug", "wholePutamen_mc", "wholeCaudate_mc", "VS_mc"))


# putamen
aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ, observed = "wholePutamen_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
    eta.partial.SS(dfm = summary(aov)[[4]]["drug","num Df"], # drug
    dfe = summary(aov)[[4]]["drug","den Df"],
    ssm = summary(aov)[[4]]["drug","Sum Sq"],
    sse = summary(aov)[[4]]["drug","Error SS"],
    Fvalue = summary(aov)[[4]]["drug","F value"],
    a = .1)[8]

    eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
    dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
    ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
    sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
    Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
    a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="MPH",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="PBO",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc:drug","num Df"], # wholePutamen_mc:drug
        dfe = summary(aov)[[4]]["wholePutamen_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(median ~ wholePutamen_mc + Error(sID/(set_size*condition_IU)), data = summ[summ$drug=="PBO",], observed = "wholePutamen_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholePutamen_mc","num Df"], # wholePutamen_mc
        dfe = summary(aov)[[4]]["wholePutamen_mc","den Df"],
        ssm = summary(aov)[[4]]["wholePutamen_mc","Sum Sq"],
        sse = summary(aov)[[4]]["wholePutamen_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["wholePutamen_mc","F value"],
        a = .1)[8]
 
        
# caudate
aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = summ, observed = "wholeCaudate_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="MPH",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="PBO",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc:drug","num Df"], # wholeCaudate_mc:drug
        dfe = summary(aov)[[4]]["wholeCaudate_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(median ~ wholeCaudate_mc + Error(sID/(set_size*condition_IU)), data = summ[summ$drug=="PBO",], observed = "wholeCaudate_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["wholeCaudate_mc","num Df"], # wholeCaudate_mc
        dfe = summary(aov)[[4]]["wholeCaudate_mc","den Df"],
        ssm = summary(aov)[[4]]["wholeCaudate_mc","Sum Sq"],
        sse = summary(aov)[[4]]["wholeCaudate_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["wholeCaudate_mc","F value"],
        a = .1)[8]  

        
# VS
aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = summ, observed = "VS_mc", factorize = FALSE)
summary(aov)
    # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]

    # comparison between MPH and PBO
    aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="SUL",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
    
    # comparison between SUL and PBO
    aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="MPH",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
    
        
    # comparison between MPH and SUL
    aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition_IU*drug)), data = summ[summ$drug!="PBO",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc:drug","num Df"], # VS_mc:drug
        dfe = summary(aov)[[4]]["VS_mc:drug","den Df"],
        ssm = summary(aov)[[4]]["VS_mc:drug","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc:drug","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc:drug","F value"],
        a = .1)[8]
        
    # PBO only
    aov <- aov_car(median ~ VS_mc + Error(sID/(set_size*condition_IU)), data = summ[summ$drug=="PBO",], observed = "VS_mc", factorize = FALSE)
    summary(aov)
        # partial eta sq + 90%CI
        eta.partial.SS(dfm = summary(aov)[[4]]["VS_mc","num Df"], # VS_mc
        dfe = summary(aov)[[4]]["VS_mc","den Df"],
        ssm = summary(aov)[[4]]["VS_mc","Sum Sq"],
        sse = summary(aov)[[4]]["VS_mc","Error SS"],
        Fvalue = summary(aov)[[4]]["VS_mc","F value"],
        a = .1)[8]    
```


Positive correlation between drug-induced effects on cognitive motivation and choice latency
```{r, fig.height=8, fig.width=8}

# calculate difference scores
ratioRedo <- summarySE(df_choice, measurevar="choice_NR", groupvars=c("sID", "drug"))
ratioRedo <- ratioRedo %>%
  dplyr::select(sID, drug, choice_NR) %>%
  spread(drug, choice_NR)
ratioRedo$MPH_effect <- ratioRedo$MPH - ratioRedo$PBO 
ratioRedo$SUL_effect <- ratioRedo$SUL - ratioRedo$PBO

RT <- summarySE(df_choice, measurevar="RT", groupvars=c("sID", "drug"))
RT <- RT %>%
  dplyr::select(sID, drug, median) %>%
  spread(drug, median)
RT$MPH_effect <- RT$MPH - RT$PBO 
RT$SUL_effect <- RT$SUL - RT$PBO

# MPH - PBO
corMPH <- cor.test(ratioRedo$MPH_effect, RT$MPH_effect) 
print(corMPH, digits = 3)
print(corMPH$p.value, digits = 3)

# SUL - PBO
corSUL <- cor.test(ratioRedo$SUL_effect, RT$SUL_effect) 
print(corSUL, digits = 3)
print(corSUL$p.value, digits =3)
   
```









